---
title: "Mid-Point Deliverable"
author: "Group AA6"
date: "5/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("scripts/chart_one.R")
source("scripts/chart_two.R")
source("scripts/summary_info.R")
```

## Summary Info Paragraph 

## Chart 1: Bar Graph
A bar graph is chosen to display the number of abortion clinics in the four
regions of the United States. This is the graph of choice because it’s able to
show the varying differences in the number of abortion clinics. It’s also ideal
because the numerical data points aren’t closely related. As shown below, the
West region has the most abortion clinics - more than 250, with the midwest
region having the least - less than 100. 

Often times, abortion clinics are closely correlated to political views. With
the west region consisting of mostly left-winged individuals who are
pro-choice, it makes sense that there are more abortion clinics in the west
compared to the midwest where more right-winged pro-life individuals reside.

``` {r, echo = F}
abortion_clinics_per_region(region_grouped)
```

## Chart 2: Scatterplot
A scatterplot was used to display the amount of total abortion clinics versus the total abortion rates based on the region. This is the graph of choice because it allows the viewer to see if there is a correlation between abortion clinics and rate in different regions.

This graph showcases that there is no correlation between the amount of abortion clinics and the amount of abortion rates per region. This means that these two factors are not codependent and influence each other. Even if there are more more abortion clinics this will not mean more people need an abortion. 

```{r, echo=FALSE}
scatterplot
```
