---
title: "Mid-Point Deliverable"
author: "Group AA6"
date: "5/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("scripts/chart_one.R")
```

## Chart 1: Bar Graph
A bar graph is chosen to display the number of abortion clinics in the four
regions of the United States. This is the graph of choice because it’s able to
show the varying differences in the number of abortion clinics. It’s also ideal
because the numerical data points aren’t closely related. As shown below, the
West region has the most abortion clinics - more than 250, with the midwest
region having the least - less than 100. 

Often times, abortion clinics are closely correlated to political views. With
the west region consisting of mostly left-winged, liberalist who are
pro-choice, it makes sense that there are more abortion clinics in the west
compared to the midwest where more right-winged conservatives pro-life
individuals reside.

``` {r, echo = F}
abortion_clinics_per_region(region_grouped)
```

