---
title: "Mid-Point Deliverable"
author: "Group AA6"
date: "5/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("dplyr")
library("knitr")
library("ggplot2")
library("leaflet")
source("scripts/chart_one.R")
source("scripts/chart_two.R")
source("scripts/chart_three.R")
source("scripts/summary_info_2.R")
source("scripts/aggregate_table.R")

```
### Midpoint Deliverable- Abortion Statistics by Region
As a group, we believe that women should have reproductive rights. We think this
would serve as an opportunity to delve into learning which reproductive resources
are provided in the United States and the differences between in each state. We
also find it interesting how there are many different sub-categories that fall
under reproductive health. These topics include abortion rate, % change in
abortion rate, change in number of clinics, % change in number of clinics,
number of abortion clinics, % of women using contraceptives. Our project is to
look specifically at the data of each region and state surrounding these topics.
You can find the source of this dataset on the
[Guttmacher Institue](https://data.guttmacher.org/states/table?dataset=data&state=AL+AK+AZ+AR+CA+CO+CT+DE+DC+FL+GA+HI+ID+IL+IN+IA+KS+KY+LA+ME+MD+MA+MI+MN+MS+MO+MT+NE+NV+NH+NJ+NM+NY+NC+ND+OH+OK+OR+PA+RI+SC+SD+TN+TX+UT+VT+VA+WA+WV+WI+WY&topics=57+283+65) and [Kaggle](https://www.kaggle.com/omer2040/usa-states-to-region). We joined these datasets to create our new dataset. 


## Summary Info Paragraph 
The dataset we used for this assignment was from the Guttmacher Institute, 
focusing on women’s reproductive health in each of the states in the USA. 
The data mainly highlights the number of abortion clinics and family planning
clinics available per state as well as the information  on the contraceptive 
usage for women aged 18-49.

For our summary table we did several calculations to find
(during the year of 2017):

 The region with the least number of clinics was the `r min_region_clinics` with a total of 
`r min_num_region_clinics` clinics in that region. The region with the most number of clinics was the `r max_region_clinics` with a total of `r max_num_region_clinics` clinics in that region. The region with the lowest percent of women using contraceptive was `r percentage_min` percent. The region with the highest percent of women using contraceptive was `r percentage_max` percent.

## Summary Table 
This table was created to very easily display the numbers of the abortion rates, Contraception Percent, and Number of Abortion Clinics in each region. We used the group_by, sum, and mean functions to compute our results for each region. We found these columns to be the most helpful for our project goal and answering our questions. Our summary table displayed that the west region had the highest contraception rate and number of abortion clinics. The midwest had the lowest abortion rate and number of abortion clinics. 
```{r, echo=FALSE}
<<<<<<< HEAD
kable(summary_table, col.names = c("Region", "Abortion Rate", "Contraception Percent", "Number of Abortion Clinics"))

=======

kable(summary_table)
#kable(joined_df, col.names = c("State", "% Change in abortion rate", "% Change in the no. of abortion #clinics","Abortion Rate", "Number of women using contraceptives", "Change in the no. of abortion clinics", "No. #of abortion clinics", "State Code", "Region", "Division"))
>>>>>>> 5c97f1399de2486421ab0b4edd30eca24ae7bedc
```

## Chart 1: Bar Graph
A bar graph is chosen to display the number of abortion clinics in the four
regions of the United States. This is the graph of choice because it’s able to
show the varying differences in the number of abortion clinics. It’s also ideal
because the numerical data points aren’t closely related. As shown below, the
West region has the most abortion clinics - more than 250, with the midwest
region having the least - less than 100. 

Often times, abortion clinics are closely correlated to political views. With
the west region consisting of mostly left-winged, liberalist who are
pro-choice, it makes sense that there are more abortion clinics in the west
compared to the midwest where more right-winged conservatives pro-life
individuals reside.

``` {r, echo = F}
abortion_clinics_per_region(region_grouped)
```

## Chart 2: Scatterplot
A scatterplot was used to display the amount of total abortion clinics versus
the total abortion rates based on the region. This is the graph of choice
because it allows the viewer to see if there is a correlation between abortion
clinics and rate in different regions.

This graph showcases that there is no correlation between the amount of
abortion clinics and the amount of abortion rates per region. This means that
these two factors are not codependent and do not influence each other.
Even if there are more more abortion clinics this will not mean more people
need an abortion. 

```{r, echo=FALSE}
scatterplot(abortion_rate_and_clinics)
```

## Char 3: Scatterplot 
This scatterplot was used to display the percentage of women aged 18 to 49 who
used contraceptives in 2017 versus the number of Abortion Clinics in a region.
We chose to do a scatterplot because it allows the viewer to easily see if there
is a correlation between the number of abortion cinlics and the percentage of
women using contraceptives. It also allows the viewer to easily see which region
that data is from.

This graph shoes that there probably is not any correlation between the number of
abortion clinics and the percentage of women taking contraceptives. This means
that the amount of abortion clinics near woemn does not seem to have any effect
on if the women will take contraceptives.

```{r, echo = FALSE}
chart_3(percent_and_clinics)
```

